Monte Carlo tree search compared to A\(^*\) in airspace configuration decision problem

### 2018-05-20 article/article.tex
(+) Added data

The graph~\ref{fig:grouping} asserts the correct behaviour of both algorithms
A\(^*\) and MCTS regarding grouping and degrouping.

Considering paragraph~\ref{ssec:theoretical_performances}, the MCTS should
eventually converge to the optimal value. This result reveals a flaw in the
implementation.

@@

>>>>

The graph~\ref{fig:grouping} asserts the correct behaviour of both algorithms
A\(^*\) and MCTS regarding grouping and degrouping. On the \(y\) axis is
indicated the number of sectors. The two algorithms show, as expected, splits
leading from 3 sectors to 5 for the MCTS to cope with the intense trafic at
the beginning of the scenario. Both algorithm choose to merge as much as
possible to go to 1 sector.

@@

\begin{figure}
  \begin{tikzpicture}
    \begin{axis}
      [line width=0.05, mark size=0.1, xlabel=depth, ylabel=cost]
      \foreach \i in {1, 2} {%
        \addplot+ table [ x index = 0, y index = \i ] {./data/cmpdepth.data};
      }
    \end{axis}
  \end{tikzpicture}
  \caption{Cost difference for varying depth with 0.5 seconds allowed to MCTS,
  \(\theta=3\)}\caption{fig:cmpdepth}
\end{figure}
